%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------

\begin{center}
    \textbf{\Huge \scshape Miguel Angel Márquez Hernández} \\ \vspace{1pt}
    \small +52 3326624029 $|$ \href{mailto:x@x.com}{\underline{marquezhdezmiguel@gmail.com}} $|$ 
    \href{https://linkedin.com/in/miguel-marquezhdz}{\underline{linkedin.com/in/miguel-marquezhdz}} $|$
    \href{https://github.com/embeddeath}{\underline{github.com/embeddeath}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Centro de Enseñanza Técnica Industrial}{Jalisco, México}
      {A.S in Electronics Engineering Technology}{Feb. 2018 -- Jul. 2022}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart


    
% -----------Multiple Positions Heading-----------
%-------------------------------------------
    \resumeSubheading
      {R\&D Embedded Software Engineer Intermediate}{September 2023 -- Present}
      {Vitesco Technologies}{Jalisco, México}
      \resumeItemListStart
        \resumeItem{Transitioned to an intermediate level role while keeping responsibilities from entry level position.}
        \resumeItem{Took part in meetings with the client to discuss requirements, testing strategies as well as debugging sessions.}
        \resumeItem{Implemented changes in fault management strategies when detecting a fault in one of the loads controlled by the ECU, modifying state machines with minimum impact to the existing code to guarantee a timely software release to the client.}
        \resumeItem{Responsible for the upkeep of four remote test benches used by the software and hardware team. This included developing tools such as python scripts that use the {\bfseries PyVisa} library to control lab equipment such as power supplies and oscilloscopes and an {\bfseries Arduino} controlled relay board that allows setting faults such as open circuit, short to ground and short to battery remotely on inductive loads controlled by the ECU to test its fault management capabilities.}
      \resumeItemListEnd
      
    \resumeSubheading
      {R\&D Embedded Software Engineer Entry}{Jul. 2022 -- Sep. 2023}
      {Vitesco Technologies}{Jalisco, México}
      \resumeItemListStart
        \resumeItem{Developed and debugged {\bfseries C code for an {\bfseries ARM Cortex M0+/M4} dual core microcontroller} using tools such as {\bfseries Lauterbach T32} software and hardware, IAR compiler, Vector network interfaces, etc.}
        \resumeItem{Implemented and tested {\bfseries ASIL-A} L2 software that supervises 4x4 shift motor behaviour and fault management. }
        \resumeItem{Took part in {\bfseries ASPICE} compliant application software development for automotive 4x4 powertrains, collaborating effectively with software, hardware and systems engineers.  }
        \resumeItem{Developed script filters for {\bfseries DOORS} that assessed the project's software requirements traceability status and enabled the project to achieve ASPICE level 2.}
        \resumeItem{Developed a scalable {\bfseries CAPL} test script template that allows granular control of all of the incoming CAN signals to an ECU. This helped reproducing and fixing timing related bugs such as race conditions caused by undesired dependencies when processing {\bfseries CAN signals.} }
    \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{ICD Alert} $|$ \emph{AVR, C, I2C/UART/Bluetooth, Hardware Design, PCB development}}{June 2022 (Graduation project)}
          \resumeItemListStart
            \resumeItem{Prototype design for a battery-powered remote monitoring system for children that suffer from congenital insensitivity to pain. The device is able to measure body temperature, and detect if the patient has fallen, alerting the parents of the status of the child. }
            \resumeItem{Developed the prototype from scratch, including low level drivers for an {\bfseries I2C} MMA845X accelerometer, {\bfseries UART} drivers for interfacing of an HC05 module, {\bfseries ADC} drivers to take readings for an LM35 temperature sensor, as well as using signal processing algorithms for signal conditioning. }
            \resumeItem{Developed the project's hardware, including schematic capture, PCB, power supply design and a 3D printed enclosure.}
            \resumeItem{Development of an Android application using MIT app inventor that interfaced with the device and received information via Bluetooth.}
            \resumeItem{Documented the project in a proper engineering thesis including design decisions and testing strategies. }
          \resumeItemListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: C, Python} \\
     \textbf{Developer Tools}{: Lauterbach Trace32, Vector CANape, Vector CANalyzer IBM Rational Doors, MKS, Git} \\
     \textbf{Embedded/Automotive Skills}{: ARM architecture knowledge, schematic diagram capture and interpretation, digital and analog electronics knowledge,CAPL scripting, ASPICE knowledge, ISO26262 awareness, CAN protocol awareness, UDS protocol awareness, I2C and UART protocol knowledge, CMake } \\

    }}
 \end{itemize}


%-------------------------------------------
\end{document}
